First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-06-08 eg6-letters/coherent/dvcs_he4_prl.tex
Add full CLAS author list

\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
\newcommand*{\ANLindex}{1}
\affiliation{\ANL}
\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\newcommand*{\ORSAYindex}{2}
\affiliation{\ORSAY}
\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\JLABindex}{3}
\affiliation{\JLAB}
\newcommand*{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand*{\ODUindex}{4}
\newcommand*{\INFNGE}{INFN, Sezione di Genova, 16146 Genova, Italy}
\newcommand*{\INFNGEindex}{5}
\newcommand*{\LPSC}{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
\newcommand*{\LPSCindex}{6}
\newcommand*{\UTFSM}{Universidad T\'{e}cnica Federico Santa Mar\'{i}a, Casilla 110-V Valpara\'{i}so, Chile}
\newcommand*{\UTFSMindex}{7}
\newcommand*{\MISS}{Mississippi State University, Mississippi State, MS 39762-5167}
\newcommand*{\MISSindex}{8}
\newcommand*{\VIRGINIA}{University of Virginia, Charlottesville, Virginia 22901}
\newcommand*{\VIRGINIAindex}{9}
\newcommand*{\VIRGINIATECH}{Virginia Polytechnic Institute and State University, Blacksburg, Virginia, 24061}
\newcommand*{\VIRGINIATECHindex}{10}

\newcommand*{\NOWJLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\NOWODU}{Old Dominion University, Norfolk, Virginia 23529}
 %%%%%%%%%%%%%%% END OF Latex Macros for institute addresses  %%%%%%%%%%%%%%%%%%%%%%%%%

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {R.~Dupr\'{e}} 
\email[corresponding author: ]{dupre@ipno.in2p3.fr}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {K.~Hafidi} 
\affiliation{\ANL}
\author{S.~Stepanyan}
\affiliation{\JLAB}
\author {S.~Bultmann} 
\affiliation{\ODU}
\author{R.~De~Vita} 
\affiliation{\INFNGE}
\author {A.~El~Alaoui} 
\affiliation{\ANL}
\affiliation{\UTFSM}
\author {L.~El~Fassi} 
\affiliation{\MISS}
\author{H.~Egiyan}
\affiliation{\JLAB}
\author{F.X.~Girod} 
\affiliation{\JLAB}
\author {M.~Guidal} 
\affiliation{\ORSAY}
\author{D.~Jenkins}
\affiliation{\VIRGINIATECH}
\author{S.~Liuti} 
\affiliation{\VIRGINIA}
\author{Y.~Perrin}
\affiliation{\LPSC}
\author {B.~Torayev} 
\affiliation{\ODU}
\author {E.~Voutier} 
\affiliation{\LPSC}
\affiliation{\ORSAY}

\collaboration{The CLAS Collaboration}
\noaffiliation

%
\date{\today}
\begin{abstract}
We report on the first measurement of the beam-spin asymmetry in the exclusive 
process of coherent deeply virtual Compton scattering off a nucleus. The 
experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
Lab incident on a pressurized $^4$He gaseous target placed in front of the CEBAF Large Acceptance 
Spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
exclusivity of the process, a specially designed radial time projection chamber 
was used to detect the recoiling $^4$He nuclei. We measured beam-spin 
asymmetries larger than those observed on the free proton in the same kinematic 
domain. From these, we were able to extract, in a model-independent way, the 
real and imaginary parts of the only $^4$He Compton form factor, $\cal H_A$. 
This pioneering measurement of coherent deeply virtual Compton scattering on 
the $^4$He nucleus, with a fully exclusive final state via nuclear recoil 
tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

>>>>

\input author_list.tex
%
\date{\today}
\begin{abstract}
We report on the first measurement of the beam-spin asymmetry in the exclusive 
process of coherent deeply virtual Compton scattering off a nucleus. The 
experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
Lab incident on a pressurized $^4$He gaseous target placed in front of the CEBAF Large Acceptance 
Spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
exclusivity of the process, a specially designed radial time projection chamber 
was used to detect the recoiling $^4$He nuclei. We measured beam-spin 
asymmetries larger than those observed on the free proton in the same kinematic 
domain. From these, we were able to extract, in a model-independent way, the 
real and imaginary parts of the only $^4$He Compton form factor, $\cal H_A$. 
This pioneering measurement of coherent deeply virtual Compton scattering on 
the $^4$He nucleus, with a fully exclusive final state via nuclear recoil 
tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}
